### 2023-11-30 docs/results.qmd
Export figure as pdf for future use
Perform time-series decomposition, specified for the daily, weekly, and monthly data

@@

## Descriptive analysis

@@

@@

@@

>>>>

options(digits = 2)

@@

## Descriptive analysis of the raw data

@@

```{r}
#| tbl-cap: Mean difference of all metrics before and during COVID-19

tar_read(desc_ts) %>% knitr::kable()

@@

### Paired plot of all metrics for each medication group

tar_read(plt_pair)

@@

## Descriptive analysis of the deseasonalized data

tar_read(plt_decom_ts_day_1.week_classic_n_claim)
tar_read(plt_decom_ts_day_1.week_classic_claim2patient)
tar_read(plt_decom_ts_day_1.week_classic_eigen)

tar_read(plt_decom_ts_week_1.month_classic_n_claim)
tar_read(plt_decom_ts_week_1.month_classic_claim2patient)
tar_read(plt_decom_ts_week_1.month_classic_eigen)

tar_read(plt_decom_ts_month_1.year_classic_n_claim)
tar_read(plt_decom_ts_month_1.year_classic_claim2patient)
tar_read(plt_decom_ts_month_1.year_classic_eigen)
